The \dealii Library, Version 9.4

### 2022-06-27 9.4/paper.tex
Use midrule

\begin{table}
  \caption{\it Timing of various particle operations for tutorial program \texttt{step-68} (particle advection in a 2D, Cartesian box) using 400,000 particles on a single process.}
  \label{tab:particle_timing}
  \centering
  \begin{tabular}{lccc}
    \toprule
    Particle Operation & \dealii 9.3 & \dealii 9.4 & Speedup      \\[0.3em]
    Generation         & 444 ms      & 235 ms      & 1.9$\times$  \\
    Iteration          & 4.18 ms     & 0.638 ms    & 6.6$\times$  \\
    Advection          & 37.8 ms     & 33.9 ms     & 1.15$\times$ \\
    Sorting            & 21.9 ms     & 9.27 ms     & 2.4$\times$  \\
    \bottomrule
  \end{tabular}
  \end{table}

@@

  \begin{tabular}{llcc}
    \toprule
    Version       & MPI routine used                     & 1 file, striping 16 & 16 files, no striping \\[0.3em]
    \dealii{} 9.3 & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s               \\
    \dealii{} 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s               \\
    \bottomrule
\end{tabular}

>>>>

\begin{table}
  \caption{\it Timing of various particle operations for tutorial program \texttt{step-68} (particle advection in a 2D, Cartesian box) using 400,000 particles on a single process.}
  \label{tab:particle_timing}
  \centering
  \begin{tabular}{lccc}
    \toprule
    Particle Operation & \dealii 9.3 & \dealii 9.4 & Speedup      \\ \midrule
    Generation         & 444 ms      & 235 ms      & 1.9$\times$  \\
    Iteration          & 4.18 ms     & 0.638 ms    & 6.6$\times$  \\
    Advection          & 37.8 ms     & 33.9 ms     & 1.15$\times$ \\
    Sorting            & 21.9 ms     & 9.27 ms     & 2.4$\times$  \\
    \bottomrule
  \end{tabular}
  \end{table}

@@

  \begin{tabular}{llcc}
    \toprule
    Version       & MPI routine used                     & 1 file, striping 16 & 16 files, no striping \\\midrule
    \dealii{} 9.3 & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s               \\
    \dealii{} 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s               \\
    \bottomrule
\end{tabular}
